---
title: "WP-4-Projecting Data"
author: "Afful Fosu"
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
  github_document: default
  html_notebook: default 
---

## Introduction
This notebook deals with 

Working with projections st_transform()
projecting points with  st_as-sf()
saving geometric data with .geojson file 
## Dependencies
This notebook requires..

```{r load-packages}
# tidyverse packages
library(dplyr)       # data wrangling
library(readr)       # read csv files
library(stringr)     # string tools
library(ggplot2)       # static mapping

# Special packages
library(mapview)      # preview spatial data
library(sf)           # spatial tools
library(tidycensus)  # demographic data
library(tigris)      # tiger/line data

# Other packages
library(here)        # file path management
library(janitor)     # data wrangling
library(naniar)      # missing data analyses
library(viridis)      # viridis color palettes
library(here)       # file path tools
library(measurements)
```

## Load Data
This notebook requires...

```{r load-data 1}
crime <- read_csv(here("data", "clean", "Crimes.csv"))
```


```{r load-data2}
 STL_SBD<-st_read(here("data","St.Louis SBD" ,"SBD","SBD.shp"))
```


## Part 1
## Data Cleaning Notes


## Part 2


homicide and removing all irrelevant records. 
```{r p1-q1}
filter(crimes_names, description %in% c("HOMICIDE")) -> homicides_unprojected

#print tibble
homicides_unprojected
```


homicide and removing all irrelevant records. 
```{r p2-q2}
filter(homicides_unprojected, x_coord != 0.0) -> homicides_clean

#print tibble
homicides_clean
```


## Project Data
 
```{r project}
homicides_sf <- st_as_sf(homicides_clean, coords = c("x_coord", "y_coord"), crs="ESRI:102696")
```


```{r preview}
 mapview(homicides_sf)
```

## Transform Projection

```{r convert-to-state-plane-m}
homicides_statePlane <- st_transform(homicides_sf, crs = 4326)
```



```{r preview st}
 mapview(homicides_statePlane)
```

check projection

```{r check projection 1}
 st_crs(homicides_statePlane)
```

Write geojson

```{r p2-pp}
st_write(STL_SBD, here("data","STL_SB.geojson"),delete_dsn= TRUE)
```


```{r p3-q3}
st_write(homicides_statePlane, here("data","final", "homicides_final.geojson"),delete_dsn= TRUE)
```


```{r p4-q4}
st_write(poverty_names, here("data","poverty_names.geojson"),delete_dsn= TRUE)
```


```{r p5-q5}
st_write(race_names, here("data","race_names.geojson"), delete_dsn= TRUE)
```


```{r p6-q6}
st_write(race_names, here("data","race_names.geojson"), delete_dsn = TRUE)
```


A description of the results.
I have uploaded my two additional layers for my WP-4-Projecting data and have also clean these data save as jeoson file and into data for my mapping in ArcGIS Pro project.Moreover, my tabular data has been converted into  x and Y coordinates and geometric data already. Again the WGS 1984 coordinates system has been projected.









